RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R

### 2014-06-24 manuscripts/manuscript.Rmd
completed sentence, re-flowed paragraph

The resulting `nex` object is an R object representation of the NeXML. This is 
a native R object for representing phylogenetic trees (as well as 
character traits, and metadata), analogous to the `phylo` object from the 
popular `ape` R package `r citep(citation("ape"))`.

While R functions and packages could be written to use this `nexml` object
directly, most users will prefer to

From this object we can extract any phylogenies it contains in the
`ape::phylo` format:

>>>>

The resulting `nex` object is an R object representation of the NeXML. This is 
a native R object for representing phylogenetic trees (as well as 
character traits, and metadata), analogous to the `phylo` object from the 
popular `ape` R package `r citep(citation("ape"))`. While R functions and packages 
could be written to use this `nexml` object directly, most users will prefer to use
already existing methods provided by packages they know. From `nex` object we can 
therefore extract any phylogenies it contains in the `ape::phylo` format:
